---
title: "Data Visualization for predicting dimonds'prices based on their clarity"
author: Peiyun Zhou
output: pdf_document
---

This is an example using ggplot to visualize the data 
The Research Question is  "Does a better clarity always mean a higher sale price?""

```{r cars}
library(ggplot2) # load the library
# one way to load the dimond data
# mydata<-read.csv((file.choose())) 
# Another way to load the data
# setwd("The directory of where the file is located") # Set working directory 
mydata<-read.csv("Mispriced-Diamonds.csv",header=T,sep=",")
```

First, let's plot the relationship between the size of carat and the sale prices

```{r pressure, echo=TRUE}
ggplot(data=mydata,aes(x=carat,y=price))+
  geom_point()
```
Then, let's use different colors to show the clarity 

```{r, echo=TRUE}
ggplot(data=mydata,aes(x=carat,y=price,colour=clarity))+
  geom_point()
```

We can adjust the transparency of the dots by changing the alpha value. 

```{r, echo=TRUE}
ggplot(data=mydata,aes(x=carat,y=price,colour=clarity))+
  geom_point(alpha=0.1)
```

We will look at the diamonds that are smaller than 2 carets and add smooth lines to illustrate the patterns. Based on the plot below, we found that clarity and price is not always a positive linear relationship. Depends on how big the diamond is, the price differ based on its clarity. 

```{r, echo=TRUE}
ggplot(data=mydata[mydata$carat<2,],aes(x=carat,y=price,colour=clarity))+
  geom_point(alpha=0.1)+
  geom_smooth()
```

We can also look the price for each dimond based on their clarity and carat size

```{r, echo=TRUE}
qplot(data=diamonds,carat,price,colour=clarity,facets=.~clarity)
```
